Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-06 main.tex
first main result

We begin with the Poincar\'e operator. 
Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
\begin{align*}
    \left| \Poinc_{\mia} u(x) \right|
    &=
    \left| 
        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
%     \\&\leq 
%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
    .
\end{align*}
We recall the radial integrals 
\begin{align*}
    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    &
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
    \\&
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
    =
    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    ,
\end{align*}
where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
    \\&
    =
    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
    .
\end{align*}
% Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$. 
Here we introduce the numerical constant 
\begin{gather}\label{equation:A_Poinc}
    A_{\Poinc}(n,\mia) := \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) },
\end{gather}
which depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$.

In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) A_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n A_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
%

@@

We analyze the Bogovski\u{\i} potential operator by similar means. 
Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\mia} u(x)$ pointwise by 
\begin{align*}
    \left| \Bogov_{\mia} u(x) \right|
    &=
    \left| 
        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
    .
\end{align*}
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
% \begin{align*}
%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
%     =
%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
%     .
% \end{align*}
% We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
    \\&
    =
    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
    .
\end{align*}
% Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
Here we introduce the numerical constant 
\begin{gather}\label{equation:A_Bogov}
    A_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
\end{gather}
which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n A_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u$ is essentially bounded.
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$. 
\\

@@

We are now state the main results of this section. 
% We are in the position to establish the main results of this section.
Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
The following upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$.
However, though the space dimension $n$ and the form degree $\mia$ enter the estimates, 
namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$.

\begin{theorem}\label{theorem:bogovpoinc}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p \leq \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
        ,
        \qquad 
        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds that 
    \begin{align}
        u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \;da
        \label{math:theorem:bogovpoinc:poincare:zero}
        \\
        u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
        \label{math:theorem:bogovpoinc:poincare:k}
    \end{align}
    In particular, if $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.

@@

        \item 
        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
        \begin{align*}
            \Xi_{1} := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $U$. 
        Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
        Combining the previous estimates for $\Psi$ and $\Theta$ with interlacing inequalities for the singular values of product matrices provides 
        \begin{align*}
            \sigma_1(x) = \matnorm{ \Jacobian \Xi_{1} }
            &\leq 
            \Cfive{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}^{2}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            ,
            \\
            \sigma_2(x), \dots, \sigma_n(x) 
            &\leq 
            \Cfiveprime{n}{k}(\calT)
            :=
            (k+1)B_{T}
            \diameterratio(\calT)
            \aspectratio(T) 
            \cdot 
            B_T
            \\
            \sigma_n(x)^{-1} = \matnorm{ \Jacobian \Xi_{1}^{-1} }
            &\leq
            \Csechs{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)
            \\
            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
            &\leq 
            \Csechsprime{n}{k}(\calT)
            :=
            (k+1)
            \diameterratio(\calT)
            \aspectratio(\calT) 
            \cdot 
            B_T
            .
        \end{align*}
        We get the determinant estimates
        \begin{align*}
            |\det(\Xi_{1})|
            &\leq 
            \Cdetfive{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{1}^{-1})|
            &\leq 
            \Cdetsechs{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{1}$.

>>>>

We begin with the Poincar\'e operator. 
Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
\begin{align*}
    \left| \Poinc_{\mia} u(x) \right|
    &=
    \left| 
        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
%     \\&\leq 
%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
    .
\end{align*}
We recall the radial integrals 
\begin{align*}
    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    &
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
    \\&
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
    =
    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    ,
\end{align*}
where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
    \\&
    =
    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
    .
\end{align*}
% Here, $C_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$. 
Here we introduce the numerical constant 
\begin{gather}\label{equation:A_Poinc}
    C_{\Poinc}(n,\mia) := \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) },
\end{gather}
which depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$.

In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) C_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n C_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
%

@@

We analyze the Bogovski\u{\i} potential operator by similar means. 
Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\mia} u(x)$ pointwise by 
\begin{align*}
    \left| \Bogov_{\mia} u(x) \right|
    &=
    \left| 
        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
    .
\end{align*}
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
% \begin{align*}
%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
%     =
%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
%     .
% \end{align*}
% We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
    \\&
    =
    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
    .
\end{align*}
% Here, $C_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
Here we introduce the numerical constant 
\begin{gather}\label{equation:A_Bogov}
    C_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
\end{gather}
which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u$ is essentially bounded.
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n C_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$. 
\\

@@

We are now state the main results of this section. 
% We are in the position to establish the main results of this section.
Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
The following upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$.
However, though the space dimension $n$ and the form degree $\mia$ enter the estimates, 
namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $C_{\Poinc}(n,\mia)$ and $C_{\Bogov}(n,\mia)$.

\begin{theorem}\label{theorem:bogovpoinc}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p \leq \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
        ,
        \qquad 
        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
        &\leq 
        n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
        &\leq 
        n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds that 
    \begin{align}
        u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \;da
        \label{math:theorem:bogovpoinc:poincare:zero}
        \\
        u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
        \label{math:theorem:bogovpoinc:poincare:k}
    \end{align}
    In particular, if $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.

@@

        \item 
        We define a mapping $ \Xi_{1} : T \rightarrow \Minako = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
        \begin{align*}
            \Xi_{1} := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $\Minako$. 
        Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
        Combining the previous estimates for $\Psi$ and $\Theta$ with interlacing inequalities for the singular values of product matrices provides 
        \begin{align*}
            \sigma_1(x) = \matnorm{ \Jacobian \Xi_{1} }
            &\leq 
            \Cfive{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}^{2}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            ,
            \\
            \sigma_2(x), \dots, \sigma_n(x) 
            &\leq 
            \Cfiveprime{n}{k}(\calT)
            :=
            (k+1)B_{T}
            \diameterratio(\calT)
            \aspectratio(T) 
            \cdot 
            B_T
            \\
            \sigma_n(x)^{-1} = \matnorm{ \Jacobian \Xi_{1}^{-1} }
            &\leq
            \Csechs{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)
            \\
            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
            &\leq 
            \Csechsprime{n}{k}(\calT)
            :=
            (k+1)
            \diameterratio(\calT)
            \aspectratio(\calT) 
            \cdot 
            B_T
            .
        \end{align*}
        We get the determinant estimates
        \begin{align*}
            |\det(\Xi_{1})|
            &\leq 
            \Cdetfive{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{1}^{-1})|
            &\leq 
            \Cdetsechs{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{1}$.

        \item 
        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Minako $ by setting 
        \begin{align*}
            \Xi_{2} := \Psi \circ \Phi.
        \end{align*}
        It is bi-Lipschitz and preserves $\partial\underlying{\patch_{\calT}(S)} \setminus \partial T$. 
        Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in \underlying{\patch_{\calT}(S)}$. 
        The combination of the previous estimates for $\Psi$ and $\Phi$ with standard interlacing inequalities now lead to 
        \begin{align*}
            \sigma_1(x)
            = 
            \matnorm{ \Jacobian \Xi_{2} }
            &\leq 
            \Csieb{n}{k}(\calT)
            :=
            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
            \cdot 
            (k+1) 
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            \\
            \sigma_2(x), \dots, \sigma_n(x) 
            &\leq 
            \Csiebprime{n}{k}(\calT)
            :=
            (k+1)B_{T}
            \diameterratio(\calT)
            \aspectratio(T) 
            \cdot 
            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
            \\
            \sigma_n(x)^{-1}
            = 
            \matnorm{ \Jacobian \Xi_{2}^{-1} }
            &\leq  
            \Cacht{n}{k}(\calT)
            :=
            \left( 2 + 3 (k+1) \aspectratio(T) \right)
            \cdot 
            (k+1) 
            \aspectratio(\calT)
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            \\
            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
            &\leq 
            \Cachtprime{n}{k}(\calT)
            :=
            (k+1)
            \diameterratio(\calT)
            \aspectratio(\calT) 
            \cdot 
            \left( 2 + 3 (k+1) \aspectratio(T) \right)
            .
        \end{align*}
        We get the determinant estimates 
        \begin{align*}
            |\det(\Xi_{2})|
            &\leq 
            \Cdetsieb{n}{k}(\calT)
            :=
            \frac 1 2 
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{2}^{-1})|
            &\leq 
            \Cdetacht{n}{k}(\calT)
            :=
            2
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{2}$. 
    \end{itemize}
    The proof is complete. 
\end{proof}
